Mixture-of-tastes Models for Representing Users with Diverse Interests

### 2017-12-13 paper/paper.tex
Make dot product notation more obvious.

Formally, let $U_i$ be a $m \times k$ matrix representing the $m$ tastes of user $i$, and $A_i$ be a $m \times k$ matrix representing the affinities of each taste for representing particular items. The recommendation score for item $j$, represented by a $k \times 1$-dimensional embedding vector $e_j$, is then given by
\begin{equation}
  r_{ij} = \sigma\left(A_ie_j\right) \cdot U_ie_j + b_j,
\end{equation}
where $b_j$ is the per-item bias term, $\sigma$ the elementwise sigmoid function, $\sigma\left(A_ie_j\right)$ gives the mixture probabilities, and $U_ie_j$ the recommendation scores given by each mixture component. We assume identity variance matrices for all mixture components.

>>>>

Formally, let $U_i$ be a $m \times k$ matrix representing the $m$ tastes of user $i$, and $A_i$ be a $m \times k$ matrix representing the affinities of each taste for representing particular items. The recommendation score for item $j$, represented by a $k \times 1$-dimensional embedding vector $e_j$, is then given by
\begin{equation}
  r_{ij} = \sigma\left(A_ie_j\right) \cdot U_ie_j + b_j,
\end{equation}
where $b_j$ is the per-item bias term, $\sigma$ the elementwise sigmoid function, $\sigma\left(A_ie_j\right)$ gives the mixture probabilities, $U_ie_j$ the recommendation scores given by each mixture component, and $\cdot$ denotes the dot product. We assume identity variance matrices for all mixture components.
